Verifying Demonstrations

### 2018-08-20 paper/security-properties.tex
Prettifying a bit in security-properties

The privacy properties we need in this context are
\begin{description}
  \item[involuntary participant unlinkability] unless the participant discloses 
    the receipt (by revealing her identity), there is no link between the 
    protest data on the ledger and the identity of the participant.

  \item[involuntary witness unlinkability] unless the witness discloses the 
    receipt (by revealing her identity), there is no link between the protest 
    data on the ledger and the identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

>>>>

The privacy properties we need in this context are the following:
\begin{description}
  \item[Involuntary participant unlinkability:] unless the participant 
    discloses the receipt (by revealing her identity), there is no link between 
    the protest data on the ledger and the identity of the participant.

  \item[Involuntary witness unlinkability:] unless the witness discloses the 
    receipt (by revealing her identity), there is no link between the protest 
    data on the ledger and the identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
